---
title: "Colonic tumours - gene list"
author: "CKing"
date: "3/6/2020"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#### The ```disgenet2r``` R package contains a set of functions to retrieve, visualize and expand DisGeNET data. DisGeNET is a discovery platform that contains information about the genetic basis of human diseases (Piñero et al. 2015; Piñero et al. 2017). DisGeNET integrates data from several expert curated databases and from text-mining the biomedical literature. https://www.disgenet.org/home/

## *MeSH Unique ID for Colorectal Neoplasms: D015179*

```{r}
library(disgenet2r, lib.loc = "/usr/lib/R/site-library")
library(dplyr)
```
#### The DisGeNET score ranges from 0 to 1, and takes into account the evidence supporting the association (See more information at https://www.disgenet.org/dbinfo#score)
```{r}

data <- disease2gene( disease  = "D015179", vocabulary = "MESH",
                       database = "CURATED",
                       score    = c(0.6,1 ) )

```

```{r}
data
```

```{r}
data@qresult[["gene_symbol"]]
```

```{r}
# List them
cat(paste(paste(data@qresult$gene_symbol, collapse= "\n "), "\n"))
# convert to data.frame
found_genes <- as.data.frame(data@qresult$gene_symbol)
```
## *Display the gene names found*
```{r}
# First Remove duplicates from list 
found_genes <- found_genes %>% distinct()
found_genes
```



### Plot
```{r pressure, echo=FALSE}
plot(data,
     prop=2)
```


## *Exclude genes already on the BD panel and show final list of genes found*
```{r}
# read in BD panel
bd_list <- read.delim("/home/cathal_king/Desktop/BD_Onco_BC_Panel.txt", header = F)

# filter
results <- found_genes %>% filter(!(`data@qresult$gene_symbol` %in% bd_list$V1))
# show final list of 10 genes
results
```

```{r}
# export gene list to file
write.table(results, file = "colonic_genes.txt", sep = "\n",
            row.names = F, col.names = F, quote = F)

```
